
\cvsection{SKILLS}
\begin{itemize}
\item{Java,Servlet,Web service}%{8}
%\divider
\item{HTML,CSS,JS}%{5}
\item{Android}%{5}
\item{Basics of AngularJs}%{3}
\item {Jboss AS,Apache WS}
\end{itemize}
% \divider
%\cvskill{German}{3}


\cvsection{Education }
\cvevent{B.Tech (IT) - 7.62 CGPA}{Velammal Engineering College,Chennai}{2012 -- 2016}{}
\smallskip
\smallskip
\smallskip
\cvevent{Higher Secondary - 84.5\% }{Sethu Bhaskara Matric,Chennai}{2010 -- 2012}{}
\smallskip
\smallskip
\smallskip
\cvevent{High School - 92\% }{Sethu Bhaskara Matric,Chennai}{2010}{}
% \divider

\cvsection{Freelancer }

\smallskip
\cvinternal{Incident Management System (Aug 2017- Feb 2018)}

\begin{itemize}
\item Worked single-handedly to delivery an Android App for a client, who is based in Singapore for his college project .
\small
\item Requirement gathering , prototyping("Just-in Mind" prototyper) and delivering the source code with quality and modern features.
\small
\item Implemented FCM (Firebase Cloud Messaging) for sending notifications to different users types in the app.
\small
\item Uploaded source code and prototype in Git .
\end{itemize}


\cvsection{Awards \& Activities }
\begin{itemize}
    \item Received "Associate of the Quarter- Q1 2019" Award.
    \item Received various awards and certificates for participating various events in college symposiums.
    \item Editor and Co-ordinator - National Conference - NCRTIC'16 .
    %\item Awarded with Narotam Sekhsaria Foundation Scholarship
\end{itemize}

\cvsection{Familiar Tools }
\begin{itemize}
    \item Eclipse , Android Studio , Sublime Text
    \item Xampp , Firebase 
    \item Just-in Mind Prototyper 
    \item Xrebel , Jrebel
    \item Postman , SOAP UI , Fiddler
    \item Putty , WinSCP
    
    %\item Awarded with Narotam Sekhsaria Foundation Scholarship
\end{itemize}

\iffalse
\cvsection{Hobbies}
\begin{itemize}
    \item Watching movies.
    \item Listening songs.
    \item Playing games .
    %\item Awarded with Narotam Sekhsaria Foundation Scholarship
\end{itemize}
\fi

% \cvachievement{\faTrophy}{}{Received accolades at Atos for Best Performance in team.}
% \cvachievement{\faTrophy}{}{Received Best Debut Award at Atos. }
% %\divider
% \cvachievement{\faInstitution}{}{Won 2nd Consolation Prize for paper presented on Cognitive Radio Networks.}
% %\divider
% \cvachievement{\faGraduationCap}{}{Got Selected in "Exclusive Scholar Program" during undergrad.}
% %\divider
% \cvachievement{\faDollar}{}{Awarded with Narotam Sekhsaria Foundation Scholarship}
%\cvsection{Strengths}

%\cvtag{Hard-working (18/24)} 
%\cvtag{Persuasive}
%\cvtag{Motivator \& Leader}

%\divider\smallskip

%\cvtag{UX}
%\cvtag{Mobile Devices \& Applications}
%\cvtag{Product Management \& Marketing}


%\divider

%\cvevent{B.S.\ in Symbolic Systems}{Stanford University}{Sept 1993 -- June 1997}{}
\iffalse
\cvsection{Projects}
\cvproject{Masked Face Detection for ATM}
\begin{itemize}
\item Developed a head classifier to detect masked faces in ATM to potentially prevent the event of robbery.
\item Different camera angle, position, image quality, illumination and type of occlusion were the major challenges. Improved the existing accuracy by 20\%.
\end{itemize}
\smallskip
\cvproject{Person Tracking}
\begin{itemize}
\item Developed, modified and implemented robust object tracker by combining motion and appearance information to learn deep association metrics.
\end{itemize}
\smallskip
\cvproject{One Shot Learning}
\begin{itemize}
\item One shot learning is the promising approach to learn good feature when little data is available. 
\item Achieved 92\% accuracy on omniglot dataset using Siamese network with Bayesian optimization.
\end{itemize}
\smallskip
\cvproject{Automatic Defect Inspection of solar farm using drones}
\begin{itemize}
\item Regular inspection of solar farm due to its wide size is strenuous. 
\item Developed a model to classify and localize defect on thermal images captured by drones.
\end{itemize}
\smallskip
\cvproject{Anomaly detection using Auto-Encoders}
\begin{itemize}
\item Developed a model to learn regular patterns from sensor data and detect unusual pattern.
\end{itemize}
\smallskip
\cvproject{Early Warning Fault Detection and Identification}
\begin{itemize}
\item Developed an LSTM based model to forecast and detect outlier from sensor data. 
\item Further, classified the given signal into one of the type of outlier.
\end{itemize}
\smallskip
\cvproject{Sentiment Analysis}
\begin{itemize}
    \item Used bag-of-words, pre-trained Embedding and simple as well as bi-directional LSTM techniques for Sentiment Analysis.
\end{itemize}
\cvproject{}
\fi